### 2021-02-23 preliminaries.tex
citace k neuronkam obecne?
Improve architecture overview
Write up preliminary description of NNs

\subsection{Neural networks}

A \emph{feed-forward neural network} is a directed acyclic graph
of differentiable \emph{modules} that operate on numeric vectors.
The common modules include multiplication by a matrix, and nonlinearity such as ReLU or sigmoid.
Some of the modules are parameterized by trainable parameters or hyperparameters.
In a typical usage, the neural network is trained by \emph{gradient descent}.
In this setting, the trained network outputs a single numeric value called \emph{loss}.
Since the network is differentiable,
a gradient of the loss is computed with respect to all the trainable parameters of the network.
The gradients are typically computed by \emph{backpropagation}.
The values of the parameters are then updated by taking a small step in the direction that minimizes the loss.

\todo{Define sigmoid.}
\todo{Maybe we don't need to make GCN a preliminary; we can define it later instead.}
\todo[inline,author=FB]{GCN? Backprop?, gradient descent, loss, gradient, epoch}

>>>>

\subsection{\Acrlongpl{nn}}

A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
Each of the components of the output vector is called a \emph{unit} of the module.
The output of each module is differentiable with respect to the input.

The common modules include
the \emph{fully connected layer}, which performs an affine transformation,
and non-linear \emph{activation functions} such as the \emph{\gls{relu}} or \emph{sigmoid}.\footnote{
These are, respectively, $f(x) = \max\{0,x\}$ and $g(x) = \frac{1}{1+e^{-x}}$.}
A fully connected layer with a single unit is called the \emph{linear unit}.

Some of the modules are parameterized by numeric \emph{parameters}.
For example, the fully connected layer that transforms the input $x$ by the affine transformation $Wx + b$
is parameterized by the weight matrix $W$ and the bias vector $b$.
If the output of a module is differentiable with respect to a parameter,
that parameter is considered \emph{trainable}.

In a typical use case, the \acrlong{nn} is trained by \emph{gradient descent} on a \emph{training set} of \emph{examples}.
% Note: In case of GCN, the example is actually a set of edge matrices.
In such setting, the network outputs a single numeric value called \emph{loss} when evaluated on a \emph{batch} of examples.
The loss of a batch is typically computed as a weighted sum of the losses of the individual examples.
Since each of the modules is differentiable with respect to its inputs and trainable parameters,
the gradient of the loss in the trainable parameters
\todo{FB: Is this terminology correct?}
can be computed using the chain rule \cite{DBLP:books/daglib/0040158}.
The trainable parameters are then updated by taking a small step
against the gradient---in the direction that is expected to make the loss value smaller.
An \emph{epoch} is a sequence of iterations that updates the trainable parameters
using each example in the training set exactly once.
